Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-22 manuscript.Rmd

*Preregistration* refers to the practice of defining research questions and planning data analysis before observing the research outcomes [@NosekRevolution2018].
It serves to separate a-priori planned and theory-driven (confirmatory) analyses from unplanned and post-hoc (exploratory) analyses.<!-- CJ I removed the bit about credibility, because that requiresfurther explanation of why separating these two types results in more credible findings-->
Exploratory analyses refer to both those aimed at discovering patterns in data, and those aimed at overcoming shortcomings of confirmatory analyses that come to light after seeing the data (e.g., violations of assumptions, modifications to address poor model fit).
Researchers are faced with a myriad of choices in designing, executing, and analyzing a study, often called researchers degrees of freedom.
Undisclosed researcher degrees may be used to modify planned analyses until a key finding reaches statistical significance or to inflate effect size estimates, a phenomenon referred to as *opportunistic bias* [@decosterOpportunisticBiasesTheir2015].
Preregistration increases transparency by clarifying when and how researchers employ their degrees of freedom.
It expressly does not restrict what researchers may do to gather or analyze their data.

There are still several shortcomings to preregistration.
One is that written study plans are often multiinterpretable.
Empirical research has shown that, even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, their results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure comprehensive and specific preregistration is to impose structure by following preregistration templates [@bowmanOSFPreregTemplate2020, @bakkerEnsuringQualitySpecificity2020].
However, such templates cannot ensure full transparency because it is impossible to verbally describe every detail of an analysis for any but the most straightforward analysis.
This ambiguity causes a second problem, namely, comparing the initial plan and the resulting publication to decide if and how researchers deviated from the preregistration.
This task is difficult because it is impossible to decide without additional information weather the analysis was actually carried out differently or just described differently.
Even if researchers were faithful to the preregistration, readers may reach opposite conclusions because they have to compare two different text that may be worded differently or describe the same thing in varying levels of detail.
A third limitation is that preregistrations are susceptible to non-reproducibility, just like primary research.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great lengths in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code resulted in different test statistics than they reported initially (see their Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g., if it includes reciprocal paths between variables or more parameters than observed data.
Conversely, a model may be misspecified in a major way; for example, by omitting direct effects when the research question is about mediation, thus leading to a model with an unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.

The workflow described in this paper facilitates a rigorous solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *Preregistration as Code (PAC)*.
PAC has the potential to eliminate undisclosed researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it reduces overhead by obviating the need to write a separate preregistration and manuscript.
For PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This already includes most of the typical sections, such as introduction, methods, and results.
These results are initially based on simulated data with the same structure as the data the authors expect to obtain from their experiments.
For guidance on how to simulate data, see @morrisUsingSimulationStudies2019, @paxtonMonteCarloExperiments2001, and @skrondalDesignAnalysisMonte2000, as well as the R packages [`simstudy`](https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html), [@simstudy] and [`psych`](https://personality-project.org/r/psych/help/sim.html), [@psych].

Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results section to the final version.
Reproducibility is of utmost importance at this stage since the preregistration must produce valid results at two points in time, once before data collection and once after data collection.
As outlined before, reproducibility builds upon four pillars (version control, dynamic document generation, dependency tracking, and software management).<!-- CJ I don't understand why you repeat this here. Remove?-->
To use PAC the dangers to reproducibility we described must be  eliminated.<!-- CJ I don't understand why you repeat this here. Remove?-->

@@

We believe that pairing PAC with the workflow presented above offers several advantages over classical preregistration.
First, PAC is merely an intermediate stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating, two separate documents.
Relatedly, writing the preregistration in the form of a research article has the advantage that researchers are usually familiar with this format.
By contrast, a preregistration template is a novelty for many.
Second, PAC is a tool for study planning.
A study can be carried out more efficiently if all steps are documented clearly than when every step is planned ad hoc.
Third, PAC removes ambiguity regarding the translation of verbal analysis plans into code.
PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
Evaluating the intended analysis code on simulated data will help identify missing steps or ambiguous decisions.
PAC therefore minimizes undisclosed researchers degrees of freedom more effectively than standard preregistration does [@bakkerEnsuringQualitySpecificity2020; @wichertsDegreesFreedomPlanning2016].
Fourth, despite its rigor, PAC accommodates partly exploratory data-dependent decisions.
Some decisions can be anticipated and formulated as conditional code.
Researchers can, for example, formulate conditions (e.g., in the form of if-else-blocks) under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods; or, an analysis may perform automated variable selection mechanisms before running the final model.
Some necessary deviations from the preregistration only become apparent after seeing the data.<!--CJ I merged point 5 here; it's part of point 4-->
Version control makes it possible to commit specific changes to the planned analyses.
It is recommended to documented all such changes by maintaining a changelog, and referencing specific commits.<!--CJ I do this myself, I think it's a good idea.-->
Another example of data-dependent decisions are more explorative analyses, i.e. explorative factor analysis or machine learning.
Decisions that do not lend themselves to formulation in code, e.g. visual inspection, must still be described verbally or be treated as noted in the next section.
With PAC researchers can precisely calibrate how much they want to explore.<!--CJ This is vague-->
When communicating a finding as explorative, it may still make a difference if tens or hundreds of variables were considered.<!-- CJ Not clear what this refers to; you haven't given an example or anything! Cut?-->

@@

Deviations from the preregistration are sometimes maligned, as if encountering unexpected challenges invalidates a carefully crafted study [@szollosi_is_2020].
However, we share the common view that deviation from a preregistration is not a problem [@nosekPreregistrationHardWorthwhile2019];
rather, a faillure to disclose such deviations is a problem.
In fact, it is expected that most PACs will require some modification after empirical data becomes available.
Often, deviations provide an opportunity to learn from the unexpected.
Transparency is essential in this regard <!--CJ: it is not clear how the following argument justifies the need for transparency. Please fix--> because an empirical test of a theory can not test the theory alone but tests it in conjunction with auxiliary assumptions [@meehlTheoreticalRisksTabular1978].

For example, imagine that authors preregistered their intention to include both "working memory" and "fluid intelligence" as covariates in an experimental study, examining the effect of task novelty on reaction time.
When evaluating the planned analyses on the empirical data, these two covariates reveal high collinearity, thus biasing estimates and compromising statistical inference.
The authors decide to use PCA to extract common variance related to "intelligence", and include this component as a covariate instead.
This change pertains to an auxiliary assumption (that working memory and fluid intelligence are distinct constructs), but does not undermine the core theory (that task novelty affects reaction time).
Now imagine that a different researcher is interested in the structure of intelligence.
This change to the preregistration directly relates their theory of intelligence.
That researcher might thus interpret the same result as an explorative finding, suggesting that these aspects of intelligence are unidimensional.
<!--CJ not sure what this final line intended to argue. I removed it. Feel free to add a more satisfactory conclusion to this paragraph-->

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind involves rigorous exploration using methods that are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit <!--CJ reference Hastie & Tibshirani-->.

## How to Write a Good PAC

When planning a study and writing a PAC, researchers ought to strive to meet three goals:<!--CJ: None of these goals relate explicitly to code. Is that a problem? Also: Shouldn't you mention the goals when you first introduce PAC?-->
First, the plan should be comprehensive.
That is, researchers need to state the research question and describe the study design and analysis in detail.
Second, the plan should be effective, meaning that the researchers should reasonably expect it to answer the research question at hand.
Third, the plan should be efficient; i.e., it should only require the necessary amount of resources.

### Comprehensiveness

Standards for scientific writing are designed to result in understandable and comprehensive research articles and can serve the same purpose for writing a preregistration.
For example, the APA standards [@apa7] require research articles describe a study in such detail that any researcher that is familiar with the field is able to repeat it.
These well-known standards thus provide a good starting point for the structure of a PAC.<!--CJ What are you arguing here? You've just convinced the reader that existing templates are not comprehensive enough. Now you're arguing that APA7 can be considered a preregistration template, and that it is comprehensive? I am a little confused here--> 
One particular advantage is introduction's and theoretical background's embedding in existing literature where that provide the basis for the study's design.<!--CJ This sentence has been missed by the language editor-->
Further inspiration may be taken from preregistration templates relevant to the type of study at hand,
because such templates address methodological rigor more comprehensively.
One factor that limits the comprehensiveness of published scientific reports is the word count imposed by journals.
If this is a concern, we suggest relegating the PAC to a reproducible appendix to keep the core manuscript concise.

Simulating data offers further benefits in ensuring the comprehensiveness of a preregistration.
It forces the researcher to consider conceptual data-analytic challenges before obtaining empirical data [@axelrodAdvancingArtSimulation1997].
It also allows researchers to verify that planned analyses are feasible and likely to run without failure [@braiekTestingMachineLearning2020] (e.g., does the code also work with missing values, extreme outliers, etc.).
Many errors and omissions are likely to come to light when evaluating the intended analysis code on simulated data.

One final method to ensure comprehensivenes of the PAC is peer review.
The value of PAC would be further enhanced by submitting it as a registered report,
a format in which articles are accepted for publication "in principle" based on peer review of the preregistered study plans [@nosekRegisteredReports2014; @chambersWhatNextRegistered2019].
In such registered report peer-reviewing a manuscript-styled PAC may well make it easier for the reviewers that ascertain and evaluate a comprehensive study plan.
Moreover, reviewers can suggest specific improvements to the planned analysis code.

### Effectiveness

If the comprehensiveness criterion is met, researchers can further check whether the planned analyses are effective.
Effectiveness can be defined in terms of ability to recover true population parameters, or power to detect a population effect.<!--CJ You have not said anything about a simulation yet, so this is kind of surprising-->.
Effectiveness can be assessed by means of a simulation study.
Once code has been written to simulate synthetic data, it is often a minor step to perform a simulation study.
It is sufficient to repeat the planned analyses many times, and plot the distribution of estimated parameters, or tabulate the proportion of replications in which a true effect was detected (power analysis).
The R command `replicate()` can be used to this end.
If an analysis fails to consistently recover the population parameters under simulated (idealized) conditions,
it would be unreasonable to expect this analysis to be effective under realistic conditions.
Because the simulation describes the researchers' expectations about real-world conditions,
it is the best way to assess the effectiveness of the analysis prior to collecting empirical data.
Simulating data requires researchers to explicate their assumptions about the data-generating mechanism in concrete computational terms; e.g. assumptions about the distributions of variables and how they relate to one another.
If a researcher experiences difficulty in specifying such assumptions, this may indicate that further literature research or exploratory pilot studies are required.

### Efficiency<!-- CJ I do not understand how 'efficiency' is different from effectiveness above. You cannot assess effectiveness by means of a single iteration. Moreover, efficiency has a specific statistical definition (pertaining to the amount of information required to estimate a parameter). Using this term can be highly confusing to our (probably statistically inclined) readership.-->

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis may help researchers to invest resources more efficiently.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

### Planned Analyses as Functions

@@

It is difficult to write analysis code when it is not clear what the expected data will look like.
We therefore recommend first simulating a dataset that resembles the expected structure of the empirical data that will be used for the final analysis.
Dedicated packages to simulate data for specific analyses exist <!--CJ Reference here-->.
For linear models, simulating data is extremely simple:

```{r}
simulate_data <- function(n, effect_size){
  # Draw n samples from a normal distribution for predictor X
  x <- rnorm(n)
  # Calculate dependent variable Y as a function of population effect size and residual error
  y <- effect_size * x + rnorm(n)
  # Return a data.frame
  data.frame(x = x, y = y)
}
simulate_data(5, .2)
```

@@

Next, write a function to conduct the planned analysis.
This function should receive the data and compute all relevant results from it.
In the simplest case, an analysis function might already exist in R.
For the linear model above, the analysis function might be:

```{r}
lm(y ~ x, data = simulate_data(5, .2))
```

The general format of an analysis function might be:

```{r}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. `return(results)`
}
```

@@

The simplest method is to collect empirical data first, but set it aside and proceed with a copy of the data that is blinded by randomly shuffling the order of rows for each variable (independently of each other).
Shuffling removes any associations between variables, while retaining information about the level of measurement and marginal distribution of each variable.
If the hypotheses pertain to associations between variables, this treatment should thus be sufficient to revent cross-contamination.
The researcher can still access the information about means or proportions (e.g., the number of participants belonging to group "A" are in the dataset), but remain uninformed about relations between variables (e.g., members of group "A" have a greater mean in variable "Z").
<!-- CJ: This is really a different issue. You should not bring it up in relation to alternatives to simulated data. Preregistration after data collection is common for secondary data analysis of data obtained by other research groups [@westonRecommendationsIncreasingTransparency2019] but not so much within the same research project.
We argue that it is still an eligible preregistration.-->
Guidelines for clinical trials already recommend analysis of blinded data  to test the feasibility of a preregistration [@ICH1998].

Another alternative to simulated data is to conduct a pilot study [@thabaneTutorialPilotStudies2010] and use the pilot data to develop the preregistration.
A pilot study has obvious advantages for study planning, since it lets the researcher evaluate the feasibility of many assumptions.
However, we must warn our readers, that while piloting is more traditional than our approach of blinding the data before preregistration, it is not innocuous to use the data resulting from the pilot study.<!--CJ What do you mean: innocuous!?-->

@@

PAC is applicable to every study that can be preregistered and ultimately uses computer code for the statistical analysis.
<!-- This is all repetition of the rest of the paper. Cut it.
The only difference is that PAC demands a comprehensive and complete analysis plan.
With traditional preregistration, researchers may (unintentionally) omit details and thus introduce decisions that appear to be made after having seen the data.
We emphasize again that deviations from the preregistration are not only possible but likely.
The advantage of PAC is transparency.
All deviations from the planned analysis as implemented in code are tracked, and the final analysis can be easily compared to the PAC.
Importantly, we see PAC as a means to increase transparency not as a means to limit researchers in their statistical analyses.
In practice, researchers may not feel ready to decide on every detail of the analysis plan before data collection.
In such cases, we recommend making decisions based on the best available knowledge, and if these decisions still prove infeasible, make simple assumptions and revise and explain them later as described in Section [Deviating from the preregistration and exploration] in the final manuscript.-->
Two types of preregistrations are particularly amenable to PAC.
First, pregistrations of clinical trials (called statistical analysis plans, @ICH1998) typically describe analyses in exhaustive detail and typically contain a detailed description of how results will be presented, including shells of tables and graphics [@yuanGuideStatisticalAnalysis2019].
PAC may significantly reduce the required workload while maintaining (and exceeding) the required standards for preregistering a clinical trial.
Second, preregistering exploratory statistical models (i.e., those with large numbers of competing models or those inspired by machine learning) is hardly feasible with standard preregistrations since they are too complex to describe and depend strongly on their software implementation.
PAC, however, captures the precise algorithmic model, including its software implementation and is ideal for preregistering these models [@brandmaier22mlsem].

@@

This example of a preregistration covers a single study with a single hypothesis.
To organize studies with multiple hypotheses, we suggest multiple `planned_analysis()` and `report_analysis()` functions (possibly numbered in accordance with the hypotheses, e.g. 1.2, 2.3 etc.).
<!--CJ I would skip this. It is a recommendation rooted in computer science, but without explaining it further, resears will not understand the motivation. Computational steps that apply to multiple analyses should be extracted into their own function, for example, those that perform data cleaning or extract results from a statistical model in an identical way.-->
Preregistrations that cover multiple distinct data sources may employ multiple `simulate_data()` functions.
These are merely suggestions, and researchers are encouraged to find their own way of how to best organize their analysis code.

@@

After researchers are satisfied with their draft preregistration, they should archive a time-stamped and indelible version of the project that serves as the preregistration.
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artefacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.org.
You may log into zenodo.org through your GitHub account.
To log in with your GitHub account:

@@

This move away from software that has served researchers well for decades is understandably difficult and presents us with a conundrum.
On the one hand, we firmly believe that automated reproducibility makes research more productive and collaboration easier.
But, on the other hand, we expect researchers to invest considerable time in learning new tools and to persuade their collaborators to do the same.
Three arguments reconcile this apparent paradox.
First, this change will not happen all at once.
Automated reproducibility is an ideal that we believe has many advantages, but it is not an all-or-nothing decision.
Researchers can pick up one skill at a time and then help their fellow collaborators to do the same.
Second, the upfront investment is required once (and efforts such as `repro` are underway to reduce it) and will pay dividends over many research projects.
Third, the move towards open software for research offers several benefits beyond enabling automated reproducibility [@schaffnerFutureScientificJournals1994; @fitzgeraldTransformationOpenSource2006; @chaldecottHistoryScientificTechnical1965; @sonnenburgNeedOpenSource2007].<!--CJ Summarize these.-->

>>>>

*Preregistration* refers to the practice of defining research questions and planning data analysis before observing the research outcomes [@NosekRevolution2018].
It serves to separate a-priori planned and theory-driven (confirmatory) analyses from unplanned and post-hoc (exploratory) analyses.
Exploratory analyses refer to both those aimed at discovering patterns in data, and those aimed at overcoming shortcomings of confirmatory analyses that come to light after seeing the data (e.g., violations of assumptions, modifications to address poor model fit).
Researchers are faced with a myriad of choices in designing, executing, and analyzing a study, often called researchers degrees of freedom.
Undisclosed researcher degrees may be used to modify planned analyses until a key finding reaches statistical significance or to inflate effect size estimates, a phenomenon referred to as *opportunistic bias* [@decosterOpportunisticBiasesTheir2015].
Preregistration increases transparency by clarifying when and how researchers employ their degrees of freedom.
It expressly does not restrict what researchers may do to gather or analyze their data.

There are still several shortcomings to preregistration.
One is that written study plans are often interpretable in multiple ways.
Empirical research has shown that, even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, their results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure comprehensive and specific preregistration is to impose structure by following preregistration templates [@bowmanOSFPreregTemplate2020, @bakkerEnsuringQualitySpecificity2020].
However, such templates cannot ensure full transparency because it is impossible to verbally describe every detail of an analysis for any but the most straightforward analysis.
This ambiguity causes a second problem, namely, comparing the initial plan and the resulting publication to decide if and how researchers deviated from the preregistration.
This task is difficult because it is impossible to decide without additional information weather the analysis was actually carried out differently or just described differently.
Even if researchers were faithful to the preregistration, readers may reach opposite conclusions because they have to compare two different text that may be worded differently or describe the same thing in varying levels of detail.
A third limitation is that preregistrations are susceptible to non-reproducibility, just like primary research.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great lengths in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code resulted in different test statistics than they reported initially (see their Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g., if it includes reciprocal paths between variables or more parameters than observed data.
Conversely, a model may be misspecified in a major way; for example, by omitting direct effects when the research question is about mediation, thus leading to a model with an unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.

The workflow described in this paper facilitates a rigorous solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *Preregistration as Code (PAC)*.
PAC has the potential to eliminate undisclosed researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it reduces overhead by removing the need to write a separate preregistration and manuscript.
For PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This already includes most of the typical sections, such as introduction, methods, and results.
These results are initially based on simulated data with the same structure as the data the authors expect to obtain from their experiments.
For guidance on how to simulate data, see @morrisUsingSimulationStudies2019, @paxtonMonteCarloExperiments2001, and @skrondalDesignAnalysisMonte2000, as well as the R packages [`simstudy`](https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html), [@simstudy] and [`psych`](https://personality-project.org/r/psych/help/sim.html), [@psych].

Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results section to the final version.
Reproducibility is of utmost importance at this stage since the preregistration must produce valid results at two points in time, once before data collection and once after data collection.
As outlined before, reproducibility builds upon four pillars (version control, dynamic document generation, dependency tracking, and software management).
To use PAC the dangers to reproducibility we described must be  eliminated.

@@

We believe that pairing PAC with the workflow presented above offers five advantages over classical preregistration.
First, PAC is merely an intermediate stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating, two separate documents.
Relatedly, writing the preregistration in the form of a research article has the advantage that researchers are usually familiar with this format.
By contrast, a preregistration template is a novelty for many.
Second, PAC is a tool for study planning.
A study can be carried out more efficiently if all steps are documented clearly than when every step is planned ad hoc.
Third, PAC removes ambiguity regarding the translation of verbal analysis plans into code.
PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
Evaluating the intended analysis code on simulated data will help identify missing steps or ambiguous decisions.
PAC, therefore, minimizes undisclosed researchers degrees of freedom more effectively than standard preregistration does [@bakkerEnsuringQualitySpecificity2020; @wichertsDegreesFreedomPlanning2016].
Fourth, despite its rigor, PAC accommodates data-dependent decisions if these can be formulated as code.
Researchers can, for example, formulate conditions (e.g., in the form of if-else-blocks) under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods; or, an analysis may perform automated variable selection mechanisms before running the final model.
Another example of data-dependent decisions are more explorative analyses, i.e. explorative factor analysis or machine learning.
Decisions that do not lend themselves to formulation in code, e.g. visual inspection, must still be described verbally or be treated as noted in the next section.
Fifth, deviations from the preregistration are clearly documented because they are reflected in changes to the code, which are managed and tracked with version control.

@@

Deviations from the preregistration are sometimes maligned, as if encountering unexpected challenges invalidates a carefully crafted study [@szollosi_is_2020].
However, we share the common view that deviation from a preregistration is not a problem [@nosekPreregistrationHardWorthwhile2019];
rather, a faillure to disclose such deviations is a problem.
In fact, it is expected that most PACs will require some modification after empirical data becomes available.
Often, deviations provide an opportunity to learn from the unexpected.

For example, imagine that authors preregistered their intention to include both "working memory" and "fluid intelligence" as covariates in an experimental study, examining the effect of task novelty on reaction time.
When evaluating the planned analyses on the empirical data, these two covariates reveal high collinearity, thus compromising statistical inference.
The authors decide to use PCA to extract common variance related to "intelligence", and include this component as a covariate instead.
This change pertains to an auxiliary assumption (that working memory and fluid intelligence are distinct constructs), but does not undermine the core theory (that task novelty affects reaction time).
Now imagine that a different researcher is interested in the structure of intelligence.
This change to the preregistration directly relates to their theory of intelligence.
That researcher might thus interpret the same result as an explorative finding, suggesting that these aspects of intelligence are unidimensional.
A deviation from preregistration thus requires a judgement about what changes affect the test of the theory [@meehlTheoreticalRisksTabular1978].
Only transparent reporting enables such judgment.

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind of exploration is through procedurally well defined exploration with exploratory statistical models are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail and researcher can therefore precisely calibrate how much they want to explore.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit [@hastieElementsStatisticalLearning2017, p. 220f.].

## Planned Analyses as Functions

@@

It is difficult to write analysis code when it is not clear what the expected data will look like.
We therefore recommend first simulating a dataset that resembles the expected structure of the empirical data that will be used for the final analysis.
Dedicated packages to simulate data for specific analyses exist <!--CJ Reference here-->.

@@

For linear models, simulating data is extremely simple:

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # Draw n samples from a normal distribution for predictor X
  x <- rnorm(n)
  # Calculate dependent variable Y
  # as a function of population effect size and residual error
  y <- effect_size * x + rnorm(n)
  # Return a data.frame
  data.frame(x = x, y = y)
}
```

Next, write a function to conduct the planned analysis.
This function should receive the data and compute all relevant results from it.
The general format of an analysis function might be:

```{r, eval=FALSE}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. `return(results)`
}
```

In the simplest case, an analysis function might already exist in R.
For the linear model above, the analysis function might be:

```{r, eval=FALSE}
planned_analyis <- function(data){
    lm(y ~ x, data = data)
}
```

@@

The simplest method is to collect empirical data first, but set it aside and proceed with a copy of the data that is blinded by randomly shuffling the order of rows for each variable (independently of each other).
Shuffling removes any associations between variables, while retaining information about the level of measurement and marginal distribution of each variable.
If the hypotheses pertain to associations between variables, this treatment should thus be sufficient to prevent cross-contamination.
The researcher can still access the information about means or proportions (e.g., the number of participants belonging to group "A" are in the dataset), but remain uninformed about relations between variables (e.g., members of group "A" have a greater mean in variable "Z").
Preregistration after data collection is common for secondary data analysis of data obtained by other research groups [@westonRecommendationsIncreasingTransparency2019] but not so much within the same research project.
We argue that it is still an eligible preregistration.
Guidelines for clinical trials already recommend analysis of blinded data  to test the feasibility of a preregistration [@ICH1998].

Another alternative to simulated data is to conduct a pilot study [@thabaneTutorialPilotStudies2010] and use the pilot data to develop the preregistration.
A pilot study has obvious advantages for study planning, since it lets the researcher evaluate the feasibility of many assumptions.
However, we must warn our readers, that while piloting is more traditional than our approach of blinding the data before preregistration, the data from the pilot study must not enter the analysis data set.

@@

PAC is applicable to every study that can be preregistered and ultimately uses computer code for the statistical analysis.
Two types of preregistrations are particularly amenable to PAC.
First, pregistrations of clinical trials (called statistical analysis plans, @ICH1998) typically describe analyses in exhaustive detail and typically contain a detailed description of how results will be presented, including shells of tables and graphics [@yuanGuideStatisticalAnalysis2019].
PAC may significantly reduce the required workload while maintaining (and exceeding) the required standards for preregistering a clinical trial.

Second, preregistering exploratory statistical models (i.e., those with large numbers of competing models or those inspired by machine learning) is hardly feasible with standard preregistrations since they are too complex to describe and depend strongly on their software implementation.
PAC, however, captures the precise algorithmic model, including its software implementation and is ideal for preregistering these models [@brandmaier22mlsem].

@@

This example of a preregistration covers a single study with a single hypothesis.
To organize studies with multiple hypotheses, we suggest multiple `planned_analysis()` and `report_analysis()` functions (possibly numbered in accordance with the hypotheses, e.g. 1.2, 2.3 etc.).
Preregistrations that cover multiple distinct data sources may employ multiple `simulate_data()` functions.
These are merely suggestions, and researchers are encouraged to find their own way of how to best organize their analysis code.

@@

After researchers are satisfied with their draft preregistration, they should archive a time-stamped and uneditable version of the project that serves as the preregistration.
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artefacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.org.
You may log into zenodo.org through your GitHub account.
To log in with your GitHub account:

@@

This move away from software that has served researchers well for decades is understandably difficult and presents us with a conundrum.
On the one hand, we firmly believe that automated reproducibility makes research more productive and collaboration easier.
But, on the other hand, we expect researchers to invest considerable time in learning new tools and to persuade their collaborators to do the same.
Three arguments reconcile this apparent paradox.
First, this change will not happen all at once.
Automated reproducibility is an ideal that we believe has many advantages, but it is not an all-or-nothing decision.
Researchers can pick up one skill at a time and then help their fellow collaborators to do the same.
Second, the upfront investment is required once (and efforts such as `repro` are underway to reduce it) and will pay dividends over many research projects.
Third, the move towards open software for research offers several benefits beyond enabling automated reproducibility [@schaffnerFutureScientificJournals1994; @fitzgeraldTransformationOpenSource2006; @chaldecottHistoryScientificTechnical1965; @sonnenburgNeedOpenSource2007].
